---
output:
  github_document:
    keep_html: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

<!-- badges: start -->
[![R-CMD-check](https://github.com/N-DucharmeBarth-NOAA/ssgrid/workflows/R-CMD-check/badge.svg)](https://github.com/N-DucharmeBarth-NOAA/ssgrid/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

<!-- <br> -->

## ssgrid: Stock Sythesis - OpenScienceGrid - utilities 

> **_Warning:_** Package is in active development. Code base may change without warning prior to first stable release.

Utility functions for running [Stock Synthesis](https://github.com/nmfs-stock-synthesis/stock-synthesis) (SS) models on the [OpenScienceGrid](https://osg-htc.org/) (OSG) [HTCondor](https://htcondor.org/) network.

This package facilitates running Stock Synthesis models and the following advanced diagnostics on the OSG:

- retrospective
- R0 likelihood profile
- age-structured production model (ASPM)
- deterministic recruitment model

The *ssgrid* contains functions for:

- connecting to the OSG
- uploading files to OSG
- writing files to automatically set-up the execution of the HTcondor job
  - creating the HTcondor *condor_submit* script
  - creating the bash shell script executed by the *condor_submit* script
  - creating R scripts needed to manipulate SS files using [r4ss](https://github.com/r4ss/r4ss) functions in order to run advanced diagnostics.
- submiting the HTcondor job
- downloading completed model runs
- cleaning up directories on OSG

## Disclaimer

Use of *ssgrid* implies adherence to the [OSG Connect and OSPool acceptable use policy:](https://portal.osg-htc.org/documentation/overview/references/policy/)

- OSG Connect may only be used for work relevant to **research and/or education** efforts associated with an academic, government, or non-profit institution in the United States.
- Proprietary data, HIPAA, and data with any other privacy concerns **should not** be stored on any OSG Connect filesystems or computed in OSG.

## Installation

*ssgrid* is not currently supported on CRAN. You can install the development version of *ssgrid* from [GitHub](https://github.com/N-DucharmeBarth-NOAA/ssgrid) with:

``` r
# install.packages("remotes")
remotes::install_github("N-DucharmeBarth-NOAA/ssgrid")
```

## Help & Documentation

Please see the *ssgrid* [webpage](https://n-ducharmebarth-noaa.github.io/ssgrid/) for more information, along with the following articles to get you started:

- [1. Setting up your OSG environment to work with *ssgrid*](https://n-ducharmebarth-noaa.github.io/ssgrid/articles/a_setup_osg.html) 
- [2. Set-up a job array to run on OSG.](https://n-ducharmebarth-noaa.github.io/ssgrid/articles/b_model_ensemble.html) This article also shows how to combine models in an ensemble using the [*ss3diags*](https://github.com/PIFSCstockassessments/ss3diags) package.
- [3. Run diagnostics for a Stock Synthesis model using OSG](https://n-ducharmebarth-noaa.github.io/ssgrid/articles/c_run_diags.html)

### Base functionality development list
- [x] base code: `osg_connect()`
- [x] base code: `osg_multi_copy()`
- [x] base code: `osg_upload_ss_dir()`
- [x] base code: `osg_wrapper_create()`
- [x] base code: `osg_condor_submit_create()`
- [x] base code: `osg_r_script_create()`
- [x] base code: `osg_execute()`
- [x] base code: `osg_monitor()`
- [x] base code: `osg_clean()` (option to just remove logs)
- [x] base code: `osg_download_ss_dir()` (download end.tar.gz, optionally download logs, and optionally remove files from osg via osg_clean after downloading)
- [x] `osg_upload_ss_dir()`: create target directory text file
- [ ] add more flexibility to input/output args
- [ ] `osg_wrapper_create()`: option to suppress log files
- [ ] `osg_wrapper_create()`: add options for running diagnostics (ASPM, retrospectives, R0 profile, jitter) via R scripts
- [ ] `osg_r_script_create()`: add options for user to pass their own R script
- [x] Documentation (roxygen2)
- [x] Make package: description, license, git-hub actions, github-pages, NOAA template
- [x] Add vignettes: setting up OSG environment
- [x] Add vignettes: launching/retrieving a job array
- [x] Add vignettes: running diagnostics across a job array
- [x] Add vignettes: model ensemble example (extracting quantities and combining with MVLN)
- [ ] Add vignettes: run with custom submit script, r script, and wrapper script


<!-- Do not edit below. This adds the Disclaimer and NMFS footer. -->

****

```{r add-disclaimer, echo=FALSE, results='asis'}
url <- "https://raw.githubusercontent.com/nmfs-fish-tools/Resources/master/Disclaimer.md"
childtext <- readLines(url)
cat(childtext, sep="\n")
```

****

```{r footer, echo=FALSE, results='asis'}
url <- "https://raw.githubusercontent.com/nmfs-fish-tools/Resources/master/footer.md" 
childtext <- readLines(url)
cat(childtext, sep="\n")
```

